**Evalution of binary classification pipelines and methods for 16S rRNA gene data**

### 2018-11-08 submission/manuscript.Rmd
shape the code better
title added

---
title: "**NAME OF THIS STUDY**"
bibliography: references.bib
output:
  pdf_document:
    keep_tex: true
    includes:
      in_header: header.tex
csl: mbio.csl #Get themes at https://github.com/citation-style-language/styles
fontsize: 11pt
geometry: margin=1.0in
---

>>>>

---
title: "**Evalution of binary classification pipelines and methods for 16S rRNA gene data**"
bibliography: references.bib
output:
  pdf_document:
    keep_tex: true
    includes:
      in_header: header.tex
csl: mbio.csl #Get themes at https://github.com/citation-style-language/styles
fontsize: 11pt
geometry: margin=1.0in
---
